Quantitative Auditing of Fairness Measures with Differentially Private Synthetic Data

### 2024-12-01 paper/paper.tex
Grouped figs togther

\section{Methodology}

@@

The dataset is first processed so it can be fed into the synthetic data generator. Some marginals are selected as described in the previous section, and the synthetic data generator model is fitted to the original data according to the marginals. Then the generator is run multiple times to obtain multiple sets of synthetic data.

@@

@@

\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{adult_mst}
\caption{Markov random field for marginals of the adult dataset.}
\label{fig:adult_mst}
\Description{Markov random field for marginals of the adult dataset.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{compas_mst}
\caption{Markov random field for marginals of the COMPAS dataset.}
\label{fig:compas_mst}
\Description{Markov random field for marginals of the COMPAS dataset.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{diabetes_mst}
\caption{Markov random field for marginals of the diabetes dataset.}
\label{fig:diabetes_mst}
\Description{Markov random field for marginals of the COMPAS dataset.}
\end{figure}

>>>>

\section{Methodology}
\label{sec:method}

@@

The dataset is first processed so it can be fed into the synthetic data generator. Some marginals are selected as described in the Section~\ref{sec:method}, and the synthetic data generator model is fitted to the original data according to the marginals. Then the generator is run multiple times to obtain multiple sets of synthetic data.

@@

% \begin{figure}[h]
%   \centering
%   \includegraphics[width=\linewidth]{adult_mst}
%   \caption{Markov random field for marginals of the adult dataset.}
%   \label{fig:adult_mst}
%   \Description{Markov random field for marginals of the adult dataset.}
% \end{figure}

% \begin{figure}[h]
%   \centering
%   \includegraphics[width=\linewidth]{compas_mst}
%   \caption{Markov random field for marginals of the COMPAS dataset.}
%   \label{fig:compas_mst}
%   \Description{Markov random field for marginals of the COMPAS dataset.}
% \end{figure}

% \begin{figure}[h]
%   \centering
%   \includegraphics[width=\linewidth]{diabetes_mst}
%   \caption{Markov random field for marginals of the diabetes dataset.}
%   \label{fig:diabetes_mst}
%   \Description{Markov random field for marginals of the COMPAS dataset.}
% \end{figure}

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.3\textwidth}
      \centering
      \includegraphics[width=\textwidth]{adult_mst}
      \caption{Markov random field for marginals of the adult dataset.}
      \label{fig:adult_mst}
      \Description{Markov random field for marginals of the adult dataset.}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
      \centering
      \includegraphics[width=\textwidth]{compas_mst}
      \caption{Markov random field for marginals of the COMPAS dataset.}
      \label{fig:compas_mst}
      \Description{Markov random field for marginals of the COMPAS dataset.}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.3\textwidth}
      \centering
      \includegraphics[width=\textwidth]{diabetes_mst}
      \caption{Markov random field for marginals of the diabetes dataset.}
      \label{fig:diabetes_mst}
      \Description{Markov random field for marginals of the COMPAS dataset.}
  \end{subfigure}
      \caption{Markov random field for marginals of the experimented datasets.}
      \label{fig:msts}
\end{figure}

@@

@@

@@
